---
layout: post
title:  "Hello, R Markdown!"
date:   2017-06-16 23:00:40 +0100
categories: r jekyll
---

You’ll find this post in your `_source` directory. Unlike the other example post on this blog (found in `_posts`), this one was written in R Markdown.

This means you can generate plots:

```{r plot}
plot(iris$Petal.Width, iris$Petal.Length,
     col = as.numeric(iris$Species) + 1,
     xlab = 'Petal Width', ylab = 'Petal Length',
     main = "Fisher's iris data")
```

And nicely-formatted tables:

```{r table, results = 'asis'}
knitr::kable(head(iris))
```

To add a new R Markdown posts, simply add a file in the `_source` directory that follows the convention `YYYY-MM-DD-name-of-post.Rmd` and includes the necessary front matter. Take a look at the source for this post to get an idea about how it works.

Want a local preview? Run
```r
source('knit.R')
```
in an R ression to compile the R Markdown files, then run `jekyll serve` on the command line to preview the site (you will need Jekyll installed for this).